\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generated PDF is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{\item\small{#1 \vspace{-2pt}}}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.15in]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Sam Pulaski} \\ \vspace{1pt}
    \small 818-590-8106 $|$ \href{mailto:sampulaski@nyu.edu}{\underline{sampulaski@nyu.edu}} $|$ 
    \href{linkedin.com/in/sampul}{\underline{linkedin.com/in/sampul}} $|$
    \href{sampul.net}{\underline{sampul.net}} $|$
    \href{https://github.com/freesampul}{\underline{github.com/freesampul}}
\end{center}

%-----------EDUCATION-----------
\section{Education}
\noindent
\begin{tabularx}{\linewidth}{X r}
    \textbf{New York University} & \textit{New York, NY} \\
    \textit{Bachelor of Arts in Computer Science} & \textit{Aug. 2024 -- Present} \\
    {\small GPA: 3.6/4.0} & \\
\end{tabularx}

\vspace{0.10cm}
{\small \textbf{Relevant Coursework:} Data Structures \& Algorithms, Computer Systems Organization, Calculus}

\vspace{0.10cm}
\noindent
\begin{tabularx}{\linewidth}{X r}
    \textbf{Harvard-Westlake School} & \textit{Los Angeles, CA} \\
    & \textit{Aug. 2018 -- Jun. 2024}
\end{tabularx}
%-----------EXPERIENCE-----------
\section{Experience}
\resumeItemListStart
  \resumeSubheading{\href{https://nsilico.net}{Nsilico}}{\underline{nsilico.net}}
  {Software Engineer and Co-Founder}{2025}
    \resumeItemListStart
      \resumeItem{Developed an LLM-powered tool to generate AI-driven survey responses tailored to diverse user personas.}
      \resumeItem{Architected and deployed the full-stack web application, enabling seamless user interaction.}
      \resumeItem{Met with 5 different VC firms: Pear VC, XFund, Beta University, Stanford BASES, NYU Ent. Labs.}
      \resumeItem{Tech stack: Next.js, TypeScript, React, Tailwind CSS, Firebase.}
    \resumeItemListEnd

  \resumeSubheading{\href{https://depicto.ai}{Depicto}}{\underline{depicto.ai}}
    {Software Engineer and Co-Founder}{2024 -- Present}
    \resumeItemListStart
      \resumeItem{Designed and built full-stack web app at HackHW (event winner).}
      \resumeItem{Developed a daily puzzle game featuring AI-generated images.}
      \resumeItem{Partnered with Blinkgame Inc. for iOS app development.}
      \resumeItem{Garnered over 1000 users, five-star rating, and media coverage.}
      \resumeItem{Achieved a 48\% user retention rate (industry average: 8\%).}
    \resumeItemListEnd

  \resumeSubheading{ZBT Fraternity Philanthropy and Recruitment}{New York, NY}
    {Fraternity Representative for NYU Panhellenic Philanthropy}{2024 -- Present}
    \resumeItemListStart
      \resumeItem{Worked as Fraternity Representative for NYU, managed over \textbf{\$40,000} annually for NYDM charity.}
      \resumeItem{Developed and executed strategic recruitment campaigns, increasing applicant numbers by 200+.}
    \resumeItemListEnd
    \resumeSubheading{Harvard-Westlake Inc.}{Los Angeles, CA}
    {Leader}{June 2018 -- June 2024}
    \resumeItemListStart
    \resumeItem{Led a team to organize a one-week, intensive \textbf{business \& product development camp} for 80+ students.}
    \resumeItem{Delivered presentations on \textbf{product market fit, user research, MVP development, and competitive analysis}, teaching participants core product management principles.}
    \resumeItem{Oversaw a \textbf{\$56,000 budget}, managing logistics for dining, event planning, and operational efficiency.}
  \resumeItemListEnd

  \resumeSubheading{Jeni’s Splendid Ice Creams}{Los Angeles, CA}
    {Customer Service Associate}{June 2022 -- June 2023}
    \resumeItemListStart
      \resumeItem{Provided high-quality service in a fast-paced team environment, ensuring customer satisfaction.}
    \resumeItemListEnd
\resumeItemListEnd

%-----------PROJECTS-----------
\section{Projects}
\resumeItemListStart
  \resumeProjectHeading
      {\textbf{Emotional Shopping} $|$ \emph{Computer Vision Product Reccomendations}}{ \href{https://freesampul.github.io/EmotionalShopping/public/index.html}{\underline{Github Page}}}
      \resumeItemListStart
        \resumeItem{Used Face-api.js library to read facial expressions.}
        \resumeItem{Reccomendations of products based on a user's emotion.}
        \resumeItem{Tech stack: React, Tailwind}
      \resumeItemListEnd
  \resumeProjectHeading
      {\textbf{Git} $|$ \emph{Version Control System}}{\href{https://github.com/freesampul/Git}{\underline{Github Page}}}
      \resumeItemListStart
        \resumeItem{Recreated Git in Java with commit functionality and internal object management.}
      \resumeItemListEnd
\resumeItemListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
\resumeItemListStart
    \resumeItem{\textbf{Languages}: Java, JavaScript, React, HTML/CSS, C}
    \resumeItem{\textbf{Frameworks}: React, Node.js}
    \resumeItem{\textbf{Developer Tools}: Git, Firebase, VS Code}
\resumeItemListEnd

\end{document}